---
title: "ClaimTicket2Rev"
output: html_notebook
---

ClaimTicket2Rev produces 2 files:
1. ClaimTicket2Rev.txt
2. ClaimTicket_TXN.txt



```{r}
refresh = 0

## for Claim Ticket, amounts are reported per OLIID + Ticket Number
grp_var <- c('OLIID','TicketNumber')
```


** Read Order Line Detail data **

Getting OLI Payor, Test, Test Delivered Date data from OLIDetail


```{r Read GHI Order Line Detail Data}

#OLIDetail_TICK <- getOLIDetail('ClaimTicket', DB_source_data, refresh)
#OLIDetail_TICK <- getOLIDetail('ClaimTicket', DB_source_data, refresh)
OLIDetail <- getOLIDetail('ClaimTicket', DB_source_data, refresh)
##something wrong with reading the local file
## reading from Database: 373260 obs.
## reading from text: 356415 obs.

OLI_info <- OLIDetail %>%
            select(OLIID, Test, TestDeliveredDate, OrderStartDate,
                   CurrentTicketNumber,
                   TerritoryRegion, OrderingHCPState
                   )

CurrTicket_payor <- OLIDetail %>%
            select(OLIID, 
#                   Test, TestDeliveredDate, OrderStartDate,CurrentTicketNumber,
                   Tier1Payor, Tier1PayorName,Tier1PayorID,
                   Tier2Payor, Tier2PayorName, Tier2PayorID,
                   Tier4Payor, Tier4PayorName, Tier4PayorID,
                   FinancialCategory, QDXInsPlanCode
#                   , TerritoryRegion, OrderingHCPState
                  )

```

### Get the Test revenue from EDWDB.fctRevenue table

```{r Read GHI Revenue Data}

Revenue <- getGHIRevenue('ClaimTicket',DB_source_data, refresh)

    # exploration
    a <- c(grep("^(?i)([^(OL)])",Revenue$OLIID), grep('^OL([^0-9])',Revenue$OLIID))
    sprintf("%d rows have null Order Line Item Id", sum(is.na(Revenue$OLIID)))
    sprintf("and %d rows have unconventional Order Line Item Id i.e. OLnnn format", length(a))

    a <- grep('^9+', Revenue$TicketNumber)    
    sprintf("%d rows have null Ticket Number", sum(is.na(Revenue$TicketNumber)))
    sprintf("however, %d rows have (-1) or (999999) Ticket Number", sum(sum(Revenue$TicketNumber=='-1'),length(a)))
    
Revenue[(which(is.na(Revenue$OLIID))),'OLIID'] <- "Unknown"

```

** get Test claim data **
Get the Test Claim data from Quadax stdClaim.txt. The data is loaded every night into ODSProd01.
The sql select claim of date of service since 2015-10-01

```{r Read QDX Claim, Payment & Case Data}
Claim <- getQDXClaim('ClaimTicket',DB_source_data,refresh)
Pymnt <- getQDXPayment('ClaimTicket',DB_source_data,refresh)
Cases <- getQDXCases('QDXClaim_CaseStatus', DB_source_data, refresh)

```

** Cleaning the data **
1. drop the scenario either need checking, and not working for the OLI grain
   a. Claim without OLI reference
   b. Payment without OLI reference

2. Remove the top side adjustment from Revenue file.
   Finance are making some of the top side adjustment to actual OLIs, OLIs that fall into the same payor/country.
   A flag is utilized in 2016 to call out revenue rows of Revenue adjustment.
   New process was introduced in 2017, since then the revenue adjustment rows are not flagged.

```{r Clean data}

#Claim_wo_OLI <- Claim[(is.na(Claim$OLIID) | Claim$OLIID=='NONE'),]
Claim_wo_OLI <- nrow(Claim[(is.na(Claim$OLIID) | Claim$OLIID=='NONE'),])
print(paste (Claim_wo_OLI, " claim tickets have no OLI reference.", sep=""))
Claim <- Claim[(!((is.na(Claim$OLIID)) | (Claim$OLIID=='NONE'))),]

#Pymnt_wo_OLI <- Pymnt[(is.na(Pymnt$OLIID) | Pymnt$OLIID=='NONE'),]
Pymnt_wo_OLI <- nrow(Pymnt[(is.na(Pymnt$OLIID) | Pymnt$OLIID=='NONE'),])
print(paste (Pymnt_wo_OLI, " Payment ticket transactions have no OLI reference.", sep=""))
Pymnt <- Pymnt[(!((is.na(Pymnt$OLIID)) | (Pymnt$OLIID=='NONE'))),]


Revenue <- Revenue %>%
           dplyr::filter(Revenue$IsRevenueReconciliationAdjustment == 0)


```

** Summarize the Revenue data by OLI + Ticket Number **
```{r Summarize Revenue}
print(paste('Claim_Ticket.R : summarize Revenue numbers start',Sys.time(), sep = " "))

Summarize_Revenue_group<-
    Revenue %>%
    group_by_(.dots=grp_var) 


Summarized_Revenue <- 
    Summarize_Revenue_group%>%
    summarize(TotalRevenue = sum(TotalRevenue),
              TotalAccrualRevenue = sum(TotalAccrualRevenue),
              TotalCashRevenue = sum(TotalCashRevenue),
              TotalUSDRevenue = sum(TotalUSDRevenue),
              TotalUSDAccrualRevenue = sum(TotalUSDAccrualRevenue),
              TotalUSDCashRevenue = sum(TotalUSDCashRevenue))

OLI_Ticket_Info <-
Summarize_Revenue_group %>%
    arrange(AccountingPeriodDate) %>%
    slice(n()) %>%
    select(grp_var, Tier1Payor, Tier1PayorName,Tier1PayorID,
           Tier2Payor, Tier2PayorName, Tier2PayorID,
           Tier4Payor, Tier4PayorName, Tier4PayorID,
           FinancialCategory, QDXInsPlanCode)

print(paste('Claim_Ticket.R : summarize Revenue numbers finish',Sys.time(), sep = " "))

```


** Summarize the Claim (Charge, Payment, Adjustment, Outstanding) by OLI + Ticket Number **
Quadax provides claim charge, total amount received per ticket, total amount adjusted per ticket and current ticket balance in the Claim file.
At all time, per a ticket, the charge amount = sum of (Received amount + adjustment amount + ticket balance)

For GHI Payor Analytics report, we reverse the sign of received amount, adjustment amount. 

```{r Summarize Claim}

print(paste('Claim_Ticket.R : summarize Claim charge and outstanding numbers start',Sys.time(), sep = " "))

temp = c('ClmAmtRec','ClmAmtAdj')
for (i in seq_along(temp)) {
    Claim[temp[[i]]] <- Claim[temp[[i]]] *-1
}

# count the number of tickets issued for an OLI 
OLI_TickCnt <- Claim %>%
                 select(OLIID, TicketNumber) %>%
                 group_by(OLIID) %>%
                 summarize(TickCnt = n_distinct(TicketNumber)) %>%
                 ungroup()

## loading plyr mess up the group by in dplyr
Summarized_Claim <-
    Claim %>%
    group_by_(.dots=grp_var) %>%
    summarize(Charge = sum(TXNAmount),
#              Payment_amt = sum(ClmAmtRec),
#              Adjust_amt = sum(ClmAmtAdj),
              Outstanding = sum(ClmTickBal))

print(paste('Claim_Ticket.R : summarize Claim charge and outstanding numbers finish', Sys.time(), sep = " "))

# nrow(unique(Claim, by = c('OLIID','TicketNumber'))) # not matching - this is from data.table, returning a data.table with duplicated rows removed. This works with Keyed vector..need to read more. 
# to count # of unique combination 
# uniqueN(Claim, by = c('OLIID','TicketNumber')) # mactching number
# nrow(unique(Claim[c('OLIID','TicketNumber')])) # matching number
```

** Summarize the Payment **
For Payor Analytics, reverse the sign for all Payment TXNAmount and Adjustment (except Refund) TXNAmount.
Then summarize the payment and adjustment amounts.

OL000755178, OL000754736,OL000754587 
multi ticket: OL000613861, OL000739220, OL000740430

```{r}
print(paste('Claim_Ticket.R : summarize Payment & Adjustment numbers start',Sys.time(), sep = " "))

# flipping the sign of adjustments except Refund
a <- which((!is.na(Pymnt$GHIAdjustmentCode)) & (Pymnt$GHIAdjustmentCode != 'GH04'))
Pymnt[a,"TXNAmount"] <- Pymnt[a,"TXNAmount"] * -1

# flip the sign of Payor & Patient payment
a <- which(Pymnt$TXNType %in% c('RI',"RP"))
Pymnt[a,"TXNAmount"] <- Pymnt[a,"TXNAmount"] * -1

Summarized_Payor_Pymnt <- Pymnt[Pymnt$TXNType=='RI',] %>%
                          group_by_(.dots=grp_var) %>%
                          summarize(PayorPaid = sum(TXNAmount))

Summarized_Patient_Pymnt <- Pymnt[Pymnt$TXNType=='RP',] %>%
                            group_by_(.dots=grp_var) %>%
                            summarize(PatientPaid = sum(TXNAmount))

# calculate the total adjustment, excluding charge in error (GH04) and refund & refund reversal (GH09)
a <- which( Pymnt$TXNType %in% c('AD','AC') &
            (Pymnt$GHIAdjustmentCode != 'GH04' & Pymnt$GHIAdjustmentCode != 'GH09')
          )
Summarized_Adjustment <- Pymnt[a,] %>%
                         group_by_(.dots=grp_var) %>%
                         summarize(TotalAdjustment = sum(TXNAmount))


# calculate the subTotal per Adjustment group
a <- which(Pymnt$TXNType %in% c('AD','AC'))
temp <- melt(Pymnt[a,c(grp_var,'AdjustmentGroup','TXNAmount')], id.vars=c(grp_var,'AdjustmentGroup'))
Summarized_Adj_group <- cast(temp, ...~variable, sum, na.rm=TRUE)
Summarized_Adj_group <- dcast(Summarized_Adj_group,
                              paste(paste(grp_var,collapse = "+"),"AdjustmentGroup",sep="~"),
                              value.var = 'TXNAmount')

rm(temp)
print(paste('Claim_Ticket.R : summarize Payment & Adjustment numbers finish',Sys.time(), sep = " "))
```

```{r}
print(paste('Claim_Ticket.R : join the summarized numbers into ClaimTicket2Rev report start',Sys.time(), sep = " "))

## Genreate a report for each OLI + Ticket Number, the summary of Claim (charge & outstanding), Payment, Adjustment
ClaimTicket2Rev<-
list(OLI_info, OLI_TickCnt, OLI_Ticket_Info,
     Summarized_Revenue,
     Summarized_Claim,
     Summarized_Payor_Pymnt,Summarized_Patient_Pymnt,
     Summarized_Adjustment, Summarized_Adj_group) %>%
    Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2), .)


temp = c('Charge','Charged in Error', 'PayorPaid','PatientPaid', 'Refund & Refund Reversal',
         "TotalRevenue", "TotalAccrualRevenue", "TotalCashRevenue",
         "TotalUSDRevenue", "TotalUSDAccrualRevenue", "TotalUSDCashRevenue",
         "Outstanding",
         "All other Adjustment", "GHI Adjustment", "Insurance Adjustment", "Revenue Impact Adjustment",
         "TickCnt")
for (i in seq_along(temp)) {
    print(temp[[i]])
    a <- which(is.na(ClaimTicket2Rev[temp[[i]]]))
    ClaimTicket2Rev[a, temp[[i]]] <- 0.00
}

ClaimTicket2Rev <- ClaimTicket2Rev %>%
                   mutate(TotalPayment = PayorPaid + PatientPaid + `Refund & Refund Reversal`)
ClaimTicket2Rev <- ClaimTicket2Rev %>%
                   mutate(TotalBilled = Charge + `Charged in Error`)

### Payor information is null if Revenue Table do not have the ticket/payor information


target = 'ClaimTicket2Rev.txt'
write.table(ClaimTicket2Rev, file = paste(output_folder,target,sep=""), sep="|", row.names=FALSE, col.names=TRUE, na="")

#rm(list = ls()[grep("^Summarize*", ls())])

print(paste('Claim_Ticket.R : join the summarized numbers into ClaimTicket2Rev report finish',Sys.time(), sep = " "))

```


**Create a TXN detail jonural entry**
This is to compare with the Finance report that report the numbers by accounting period.

OLI | Ticket | TXN_Date | TXN type | TXN Line Number | TXN Currency | TXN Amount


##need Total Payment
Total Bill??

```{r TXN Detail}


# retrieve billing transactions
Claim_TTXN <- Claim %>%
             select (OLIID, TicketNumber, CaseNumber,
                     Test, OLIDOS,
                     TXNDate, TXNAcctPeriod, TXNLineNumber, TXNType,
                     TXNCurrency, TXNAmount)
setnames(Claim_TTXN, 'OLIDOS','TestDeliveredDate')

# retrieve payment transactions
Pymnt_TTXN <- Pymnt %>%
             dplyr::filter(TXNType %in% c('RI','RP')) %>%
             select(OLIID, TicketNumber,CaseNumber,
                    Test, OLIDOS,
                    TXNDate, TXNAcctPeriod, TXNLineNumber, TXNType,
                    TXNCurrency, TXNAmount)
setnames(Pymnt_TTXN, 'OLIDOS','TestDeliveredDate')


# retrieve adjustment transactions
Adjustment_TTXN <- Pymnt %>%
                  dplyr::filter(TXNType %in% c('AC','AD')) %>%
                  select(OLIID, TicketNumber,CaseNumber,
                    Test, OLIDOS,
                    TXNDate, TXNAcctPeriod, TXNLineNumber, TXNType,
                    TXNCurrency, TXNAmount,
                    QDXAdjustmentCode, Description, GHIAdjustmentCode, CategoryDesc, AdjustmentGroup)
setnames(Adjustment_TTXN, 'OLIDOS','TestDeliveredDate')

# retrieve revenue transactions
                
Revenue_TTXN <- data.table::melt(Revenue[,c(grp_var,'AccountingPeriod','AccountingPeriodDate',
                              'Currency',
                              'TotalRevenue', 'TotalCashRevenue','TotalAccrualRevenue',
                              'TotalUSDRevenue','TotalUSDCashRevenue','TotalUSDAccrualRevenue')]
                   , id=c(grp_var, 'AccountingPeriod','AccountingPeriodDate','Currency'), na.rm=TRUE)

setnames(Revenue_TTXN,
         c("AccountingPeriod","AccountingPeriodDate","Currency","variable","value"),
         c("TXNAcctPeriod","TXNDate","TXNCurrency","TXNType","TXNAmount"))

Revenue_TTXN$TXNLineNumber <- 0
Revenue_TTXN <- left_join(Revenue_TTXN, OLI_info[,c('OLIID','Test','TestDeliveredDate')])

ClaimTicket_TXN <-
list(Claim_TTXN
     ,Pymnt_TTXN
     ,Adjustment_TTXN
     ,Revenue_TTXN
    ) %>%
    Reduce(function(dtf1,dtf2) bind_rows(dtf1,dtf2), .)

ClaimTicket_TXN <- ClaimTicket_TXN %>%
                    dplyr::filter(TXNAmount != 0.0) %>%
                    #dplyr::filter(TestDeliveredDate >= '2017-06-01' & TestDeliveredDate <= '2017-07-31')%>%
                    arrange(OLIID, TicketNumber,desc(TXNLineNumber))




target = 'ClaimTicket_TXN.txt'
write.table(ClaimTicket_TXN, file = paste(output_folder,target,sep=""), sep="|", row.names=FALSE, col.names=TRUE, na="")


#rm(list = ls()[grep("*_TTXN*", ls())])

```

