---
title: "Data exploration"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

** explore QDX_PA **

priorAuthCaseNum is associated with 1 or none priorAuthTicketNumber.
e.g. Case is open pre claim Prior Authorization process before a claim ticket is issue.
Each caseNum has only 1 priorAuthReq type.

There are rows with empty priorAuthStatus. These cases either 
1. have no priorAuthStatus requirement, and the priorAuthEnteredDate is null; or 
2. the AuthEnteredDate are between 20050919 to 20091027, remove these rows with priorAuthEnteredDate < 2010 from the dataset

All case entered after 2016 have priorAuthStatus
```{r QDX PA}

    QDX_PA <- read.csv(file.path(QDX_zip_data, 'priorAuth.txt', sep=""), header=T, sep="|", stringsAsFactors = F)

    # check priorAuthCaseNum : priorAuthTicketNum
    temp <- QDX_PA %>%
            group_by(priorAuthCaseNum, priorAuthTicketNum) %>%
            summarize(TickCnt = n_distinct(priorAuthTicketNum))
    sum(temp$TickCnt>1)

    # check priorAuthTicketNum : priorAuthReq
    temp <- QDX_PA %>%
            group_by(priorAuthTicketNum) %>%
            summarize(PA_Req_cnt = n_distinct(priorAuthReq))
    a <- which(temp$PA_Req_cnt>1)
    
    temp <- QDX_PA %>%
            group_by(priorAuthCaseNum) %>%
            summarize(PA_Req_cnt = n_distinct(priorAuthReq))
    a <- which(temp$PA_Req_cnt>1)
    
    # row 279054, PT001003149 , ticketNum = 788364 , caseNum=985289, is the priorAuthNumber = '1706|AAAPF' which has the pipe character in it?
    
    a <- filter(QDX_PA, QDX_PA$priorAuthStatus == "")
    nrow(a)
    range(a$priorAuthEnteredDt)
```


** explore QDX Cases **
finding the QDX Cases - OLI - Ticket entity relationship

```{r}

    Cases <- getQDXCases('QDXClaim_CaseStatus', DB_source_data, 0)
    
    temp <- Cases %>%
            group_by(caseAccession) %>%
            summarize(QDX_Case_cnt = n_distinct(caseCaseNum))
    
    a <- temp[which(temp$QDX_Case_cnt > 1), 'caseAccession']
    
#    b <- Cases[a,c('caseAccession','caseEntryYrMth')]
    b <- Cases %>%
         dplyr::filter(caseAccession %in% a$caseAccession) %>%
         arrange(caseAccession) %>%
         dplyr::filter(caseAccession != 'NONE')

    
    Cases_temp <- left_join(Cases,temp, by='caseAccession')

    temp <- Cases %>%
            group_by(caseAccession) %>%
            summarize(QDX_Tick_cnt = n_distinct(caseTicketNum))

    Cases_temp <- left_join(Cases_temp, temp, by='caseAccession')
    
    target = 'QDX_M_Cases_OLI.xlsx'
    write.xlsx(b, file = paste(output_folder,target,sep=""), row.names=FALSE, col.names=TRUE, showNA=FALSE)

```

** Explore GHI SFDC PreBilling Cases **

```{r}

target <- 'GHI_SFDC_PreBillingCases.txt'
con <-odbcDriverConnect(connection = "Driver={ODBC Driver 13 for SQL Server};trusted_connection=yes;
                       server=EDWStage;
                       database=StagingDB")
sql <- paste(trimws(readr::read_lines(paste(sql_folder, "StagingDB_SFDC_PreBillingCases.sql",sep=""))), collapse="\n")
output <- sqlQuery(con, sql, stringsAsFactors = FALSE)
write.table(output, paste(folder, target, sep=""), row.names=FALSE, sep="|")
odbcClose(con)


    temp <- output %>%
            group_by(OSM_Order_Line_Item_ID__c) %>%
            summarize(PreBilling_Case_cnt = n_distinct(CaseNumber))
    
    a <- temp[which(temp$PreBilling_Case_cnt > 1), 'OSM_Order_Line_Item_ID__c']
    
    temp2 <- output[output$OSM_Order_Line_Item_ID__c %in% a$OSM_Order_Line_Item_ID__c,]

```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.


## 
Read the SFDC Plan

```{r SFDC Plans}

GHI_Payor_Current <- getGHIPayorMaster(output_folder, 1)

temp <- GHI_Payor_Current %>%
        group_by(QDX_Ins_Plan_Code) %>%
        count(QDX_Ins_Plan_Code)


print (paste("Number of QDX plans map to mutliple GHI Plans : ", nrow(temp[temp$n>1,]), sep=""))
```

## read the Plans provided by Quadax via FTP nightly feed


```{r pressure, echo=FALSE}
QDX_insPlans <- getQDXInsPlans(output_folder, refresh=1)
    

tempM <- left_join(QDX_insPlans, GHI_Payor_Current, by = c("insPlanCode" = "QDX_Ins_Plan_Code"))
temp2 <-tempM[is.na(tempM$Tier4Payor),]

print(paste (nrow(tempM[is.na(tempM$Tier4Payor),])," of QDX plans do not have a GHI Plan record in SFDC ",  sep=""))
```

