---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---



```{r}
# Translate QDX test code to GHI
QDX_GHI_Test_Code <- data.table(QDX_Code = c('GL','GLD','GLC','MMR','GLP','LIQSEL','UNK'),
                                GHI_Code = c('IBC','DCIS','Colon','MMR','Prostate','LIQSEL','Unknown'))
```

** GET TEST CLAIM TICKET DATA FROM QUADAX **

Get the Test Claim data from Quadax stdClaim.txt. The data is loaded every night into ODSProd01.
The sql select claim of date of service since 2015-10-01

```{r}
# read the raw data from ODSProd01
getQDXClaim <- function (usage, folder, refresh = 0) {
    
    target <- "ODSProd01_Quadax_QDX_stdClaimFile.txt"
    
    print(paste('stdClaim : reading Claim Data ',Sys.time(), sep = " "))
    if (refresh == 1) {
        con <-odbcDriverConnect(connection = "Driver={ODBC Driver 13 for SQL Server};trusted_connection=yes;
                               server=ODSProd01;
                               database=Quadax")
        #a <- trimws(readr::read_lines("./data/QDX_stdClaim.sql"))
        #sql <- paste(trimws(readr::read_lines("./data/QDX_stdClaim.sql")), collapse="\n")
        sql <- paste(trimws(readr::read_lines(paste(sql_folder, "QDX_stdClaim.sql",sep=""))), collapse="\n")
        Claim <- sqlQuery(con, sql, stringsAsFactors = FALSE)
        write.table(Claim,paste(folder,target,sep=""), sep="|",row.names=FALSE)
        odbcClose(con)
    } else {
        Claim <- read.table(paste(folder,target,sep=""), sep="|", header=TRUE, stringsAsFactors = FALSE)
    }

    print(paste('stdClaim : cleaning Claim Data ',Sys.time(), sep = " "))
    
    prep_file_name <- "QDX_ClaimDataPrep.xlsx"
    claim_note <- read.xlsx(paste(prep_file_path, prep_file_name, sep=""), sheetName ="QDXClaim", startRow=2,
                            colIndex=c(2,3:6),stringsAsFactors=FALSE)

    # rename columns
    rename_col <- match(claim_note$QDX_stdClaimFile,names(Claim))
    names(Claim)[na.omit(rename_col)] <- claim_note$Synonyms[which(!is.na(rename_col))]

    
    # Translate QDX test code to GHI
    #QDX_GHI_Test_Code <- data.table(QDX_Code = c('GL','GLD','GLC','MMR','GLP','LIQSEL','UNK'),
    #                                GHI_Code = c('IBC','DCIS','Colon','MMR','Prostate','LIQSEL','Unknown'))
    
    for (i in seq_along(QDX_GHI_Test_Code$QDX_Code)) {
        #print (QDX_GHI_Test_Code$QDX_Code[i])
        a <- which(Claim$Test == QDX_GHI_Test_Code$QDX_Code[i])
        Claim[a,'Test'] <- QDX_GHI_Test_Code$GHI_Code[i]
    }
    # table(Claim$Test)
    #a <- Claim %>%
    #       filter(Test=='GLP') %>%
    #       select(ReRoutedPrimaryInsPlan_GHICode, PrimaryInsPlanName)
    #       View(a)
    
    # Convert the dates
    Claim$TXNDate <- ymd(Claim$TXNDate)
    Claim$OLIDOS <- ymd(Claim$OLIDOS)
    
    Claim$TicketNumber <- as.character(Claim$TicketNumber)
    Claim$CaseNumber <- as.character(Claim$CaseNumber)
    
    # set the TXNLineNumber and TXNType for TXNDetail Report
    Claim <- Claim %>%
             mutate(TXNLineNumber = 0, TXNType='CL')
    
    
    # find the Payor/plan that the Claim Ticket is issued to
    # the value should come from the ReReoutedPayor. If ReReoutedPayor is blank, take from the PrimaryPayor
    QDX_Tick_Payor_map <- data.table(Ticket_payor = c('TicketInsComp_QDXCode',
                                                       'TicketInsPlan_QDXCode',
                                                       'TicketInsCompName',
                                                       'TicketInsPlanName',
                                                       'TicketInsFC',
                                                       'TicketInsComp_GHICode',
                                                       'TicketInsPlan_GHICode'),
                                     ReRoutePrimary = c('ReRoutedPrimaryInsComp_QDXCode',
                                                        'ReRoutedPrimaryInsPlan_QDXCode',
                                                        'ReRoutedPrimaryInsCompName',
                                                        'ReRoutedPrimaryInsPlanName',
                                                        'ReRoutedPrimaryInsFC',
                                                        'ReRoutedPrimaryInsComp_GHICode',
                                                        'ReRoutedPrimaryInsPlan_GHICode'),
                                        PrimaryIns = c('PrimaryInsComp_QDXCode',
                                                       'PrimaryInsPlan_QDXCode',
                                                       'PrimaryInsCompName',
                                                       'PrimaryInsPlanName',
                                                       'PrimaryInsFC',
                                                       'PrimaryInsComp_GHICode',
                                                       'PrimaryInsPlan_GHICode')
                                    )
    
    a <- which(is.na(Claim$ReRoutedPrimaryInsPlan_QDXCode))
    b <- which(!is.na(Claim$ReRoutedPrimaryInsPlan_QDXCode))
    for (i in seq_along(QDX_Tick_Payor_map$Ticket_payor)) {
        #print (paste(i, " : ", QDX_Tick_Payor_Source$Ticket_payor[i],
        #             " : ",QDX_Tick_Payor_Source$PrimaryIns[i],
        #             " : ",QDX_Tick_Payor_Source$ReRoutePrimary[i], sep=""))
        Claim[a,QDX_Tick_Payor_map$Ticket_payor[i]] <- Claim[a,QDX_Tick_Payor_map$PrimaryIns[i]]
        Claim[b,QDX_Tick_Payor_map$Ticket_payor[i]] <- Claim[b,QDX_Tick_Payor_map$ReRoutePrimary[i]]
    }
    
    print(paste('stdClaim : output Claim Data based on usage ', usage ,Sys.time(), sep = " "))
    
    if (usage == 'Claim2Rev') {
        select_columns <- claim_note[which(claim_note$Claim2Rev==1),'Synonyms']
    } else if (usage == 'ClaimTicket'){
        select_columns <- claim_note[which(claim_note$ClaimTicket==1),'Synonyms']
    }
    Claim <- select(Claim, select_columns)
    return(Claim)
}
```


** GET CLAIM TICKET TRANSACTION DATA FROM QUADAX **
These are the payment, adjustment, refund, charge error adjustment, etc data
Quadax provides a refresh of the stdPayment data. The data is loaded into ODSProd01 everyday.

```{r stdPayment}
getQDXPayment <- function (usage, folder, refresh = 0){
    
    target <- "ODSProd01_Quadax_QDX_stdPayment.txt"
    
    print(paste('stdPayment : reading Payment Data ',Sys.time(), sep = " "))
    if (refresh == 1) {
        con <-odbcDriverConnect(connection = "Driver={ODBC Driver 13 for SQL Server};trusted_connection=yes;
                               server=ODSProd01;
                               database=Quadax")
        #a <- trimws(readr::read_lines("./data/QDX_stdClaim.sql"))
        #sql <- paste(trimws(readr::read_lines("./data/QDX_stdPayment.sql")), collapse="\n")
        sql <- paste(trimws(readr::read_lines(paste(sql_folder, "QDX_stdPayment.sql", sep=""))), collapse="\n")
        Pymnt <- sqlQuery(con, sql, stringsAsFactors = FALSE)
        write.table(Pymnt,paste(folder,target,sep=""), sep="|",row.names=FALSE)
        odbcClose(con)
    } else {
        Pymnt <- read.table(paste(folder,target,sep=""), sep="|", header=TRUE, stringsAsFactors = FALSE)
    }

    prep_file_name <- "QDX_ClaimDataPrep.xlsx"
    pymnt_note <- read.xlsx(paste(prep_file_path, prep_file_name, sep=""), sheetName ="QDXPayment", startRow=2,
                            colIndex=c(2,3:8),stringsAsFactors=FALSE)

    # rename columns
    rename_col <- match(pymnt_note$QDX_stdPaymentFile,names(Pymnt))
    names(Pymnt)[na.omit(rename_col)] <- pymnt_note$Synonyms[which(!is.na(rename_col))]

    print(paste('stdPayment : cleaning and transforming Payment Data ',Sys.time(), sep = " "))
    
    # Convert the dates
    Pymnt$TXNDate <- ymd(Pymnt$TXNDate)
    Pymnt$OLIDOS <- ymd(Pymnt$OLIDOS)
    
    Pymnt$TicketNumber <- as.character(Pymnt$TicketNumber)
    Pymnt$CaseNumber <- as.character(Pymnt$CaseNumber)

    # Translate QDX test code to GHI
    #QDX_GHI_Test_Code <- data.table(QDX_Code = c('GL','GLD','GLC','MMR','GLP','LIQSEL','UNK'),
    #                                GHI_Code = c('IBC','DCIS','Colon','MMR','Prostate','LIQSEL','Unknown'))
    
    for (i in seq_along(QDX_GHI_Test_Code$QDX_Code)) {
        #print (QDX_GHI_Test_Code$QDX_Code[i])
        a <- which(Pymnt$Test == QDX_GHI_Test_Code$QDX_Code[i])
        Pymnt[a,'Test'] <- QDX_GHI_Test_Code$GHI_Code[i]
    }
    
    # Remove Allowable, Deductible and Coinsurance from Adjustment Lines
    a <- which(Pymnt$TXNType %in% c('AC','AD'))
#    Pymnt[a,c('stdPymntAllowedAmt','stdPymntDeductibleAmt','stdPymntCoinsAmt')]<-NA
    
    # Populate the PymntInsPlan_QDXCode field with QDXAdjustmentCode field for Payment Transaction (ie TXNType = RP, RI)
    a <- which(Pymnt$TXNType %in% c('RI','RP'))
    Pymnt[a,'PymntInsPlan_QDXCode'] <- Pymnt[a,'QDXAdjustmentCode']
    Pymnt[a,'QDXAdjustmentCode'] <- NA
    Pymnt[a,'GHIAdjustmentCode'] <- NA
   
    QDX_Tick_Payor_map <- data.table(Ticket_payor = c('TicketInsComp_QDXCode',
                                                      # 'TicketInsPlan_QDXCode',
                                                      # 'TicketInsCompName',
                                                      # 'TicketInsPlanName',
                                                      # 'TicketInsFC',
                                                       'TicketInsComp_GHICode',
                                                       'TicketInsPlan_GHICode'),
                                         PrimaryIns = c('PrimaryInsComp_QDXCode',
                                                       #'PrimaryInsPlan_QDXCode',
                                                       #'PrimaryInsCompName',
                                                       #'PrimaryInsPlanName',
                                                       #'PrimaryInsFC',
                                                       'PrimaryInsComp_GHICode',
                                                       'PrimaryInsPlan_GHICode')
                                    )
    a <- which(is.na(Pymnt$TicketInsPlan_QDXCode))
    for (i in seq_along(QDX_Tick_Payor_map$Ticket_payor)) {
        Pymnt[a,QDX_Tick_Payor_map$Ticket_payor[i]] <- Pymnt[a,QDX_Tick_Payor_map$PrimaryIns[i]]
    }
    
    # update an old GHI adjustment code for PRAC to GH01, Financial Assistance Adj for Financial Assistance
    a <- which(Pymnt$QDXAdjustmentCode=='PRAC' & Pymnt$GHIAdjustmentCode != 'GH07')
    Pymnt[a,'GHIAdjustmentCode'] <- 'GH07'
 
    # Resolve the adjusment code
    ## ************************
    AdjustmentCode <- read.xlsx(paste(prep_file_path, prep_file_name, sep=""), sheetName ="AdjustmentCode", header=TRUE, startRow=1,
                            colIndex=c(1,3,5,7),stringsAsFactors=FALSE)
    #temp <- merge(Pymnt, AdjustmentCode, all.x=TRUE, by.x="QDXAdjustmentCode", by.y = "Code")  ## merge not working
    Pymnt <- left_join(Pymnt, AdjustmentCode, by = c('QDXAdjustmentCode' = 'Code'))
    
    
    print(paste('stdPayment : select & return Payment Data ',Sys.time(), sep = " "))

    if (usage == 'Claim2Rev') {
        select_columns <- pymnt_note[which(pymnt_note$Claim2Rev==1),'Synonyms']
    } else if (usage == 'ClaimTicket'){
        select_columns <- pymnt_note[which(pymnt_note$ClaimTicket==1),'Synonyms']
    }
    Pymnt <- select(Pymnt, select_columns)
    return(Pymnt)
}
```

** GET CLAIM CASE STATUS FROM QUADAX **
Quadax provides the billing case status in the stdCases.txt.

```{r}
getQDXCases <- function (usage, folder, refresh = 0){
    
    target <- "ODSProd01_Quadax_QDX_claim_case_status.txt"
    
    print(paste('stdCases : reading Claim Cases status data ',Sys.time(), sep = " "))
    if (refresh == 1) {
        con <-odbcDriverConnect(connection = "Driver={ODBC Driver 13 for SQL Server};trusted_connection=yes;
                               server=ODSProd01;
                               database=Quadax")
        #a <- trimws(readr::read_lines("./data/QDX_stdClaim.sql"))
        #sql <- paste(trimws(readr::read_lines("./data/QDX_stdCases.sql")), collapse="\n")
        sql <- paste(trimws(readr::read_lines(paste(sql_folder, "QDX_Cases.sql",sep=""))), collapse="\n")
        Cases <- sqlQuery(con, sql, stringsAsFactors = FALSE)
        write.table(Cases,paste(folder,target,sep=""), sep="|",row.names=FALSE)
        odbcClose(con)
    } else {
        Cases <- read.table(paste(folder,target,sep=""), sep="|", header=TRUE, stringsAsFactors = FALSE)
    }
    
    Cases$caseUpdateDate <- ymd(Cases$caseUpdateDate)
    # adding '01' to workaround the need for date
    Cases$caseEntryYrMth <- as.Date(paste(Cases$caseEntryYrMth,'01',sep=""), format='%Y%m%d')
    Cases$caseTicketNum <- as.character(Cases$caseTicketNum)
    Cases$caseCaseNum <- as.character(Cases$caseCaseNum)
    Cases$caseAddedDateTime <- paste(Cases$caseDateAdded, " ", Cases$caseTimeAdded)
    Cases$caseAddedDateTime <-ymd_hms(Cases$caseAddedDateTime)
    
    
    prep_file_name <- "QDX_ClaimDataPrep.xlsx"
    case_note <- read.xlsx(paste(prep_file_path, prep_file_name, sep=""), sheetName ="QDXCases", startRow=2,
                            colIndex=c(2,6:9),stringsAsFactors=FALSE)
    
    if (usage == 'case_reference') {
        select_columns <- case_note[which(case_note$case_reference==1),'Synonyms']
    } else if (usage == 'QDXClaim_CaseStatus') {
        select_columns <- case_note[which(case_note$QDXClaim_CaseStatus==1),'Synonyms']
    }
    return(Cases[,select_columns])
}

```


** Get Payor and Insurance Plan code and detail mapping from QDX **

```{r}
getQDXInsPlans <- function(folder, refresh=0) {
    
    target <- "ODSProd01_Quadax_QDX_insCodes.txt"
    
    if (refresh == 1) {
        
        con <-odbcDriverConnect(connection = "Driver={ODBC Driver 13 for SQL Server};trusted_connection=yes;
                               server=ODSProd01;
                               database=Quadax")
        ##change Mar 20
        #sql <- paste(trimws(readr::read_lines(paste(sql_folder, "QDX_insCodes.sql",sep=""))), collapse="\n")
        sql <- paste(trimws(readr::read_lines(paste(sql_folder, "QDX_insPlans.sql",sep=""))), collapse="\n")
        
        QDXinsPlansCode <- sqlQuery(con, sql, stringsAsFactors = FALSE)
        write.table(QDXinsPlansCode,paste(folder,target,sep=""), sep="|",row.names=FALSE)
        odbcClose(con)
    } else {
        QDXinsPlansCode <- read.table(paste(folder,target,sep=""), sep="|", header=TRUE, stringsAsFactors = FALSE)
    }    

    QDXinsPlansCode <- QDXinsPlansCode %>%
             group_by(insPlanCode) %>%
             count(insPlanCode) %>%
             left_join(QDXinsPlansCode,.,by = c('insPlanCode'))
             
    setnames(QDXinsPlansCode,'n','row_cnt')

    # There are duplicate insPlanCode in the Quadax Master File.
    QDXinsPlansCode <- QDXinsPlansCode %>%
                      group_by(insPlanCode) %>%
                      slice(1)

        
    return(QDXinsPlansCode)
}
```

** Get prior authorization cases data
priorAuthCase 
in the virtualSelfDescInfo, line 2850 contains a special character
PL|VO|Volapk|||


```{r}
getQDXPA <- function(folder, refresh=0) {
    
    target <- "ODSProd01_Quadax_QDX_priorAuth.txt"
    
    if (refresh == 1) {
        con <-odbcDriverConnect(connection = "Driver={ODBC Driver 13 for SQL Server};trusted_connection=yes;
                               server=ODSProd01;
                               database=Quadax")
        #a <- trimws(readr::read_lines("./data/QDX_stdClaim.sql"))
        #sql <- paste(trimws(readr::read_lines("./data/QDX_stdCases.sql")), collapse="\n")
        sql <- paste(trimws(readr::read_lines(paste(sql_folder, "QDX_priorAuth.sql",sep=""))), collapse="\n")
        priorAuth <- sqlQuery(con, sql, stringsAsFactors = FALSE)
        write.table(priorAuth,paste(folder,target,sep=""), sep="|",row.names=FALSE)
        odbcClose(con)
    } else {
        priorAuth <- read.table(paste(folder,target,sep=""), sep="|", header=TRUE, stringsAsFactors = FALSE)
    }
    
    #QDX_PA <- read.csv(file.path(folder, 'priorAuth.txt', sep=""), header=T, sep="|", stringsAsFactors = F)
    
    priorAuth$priorAuthDate <- ymd(priorAuth$priorAuthDate)
    priorAuth$priorAuthEnteredDt <- ymd(priorAuth$priorAuthEnteredDt)
    
    priorAuth$priorAuthCaseNum <- as.character(priorAuth$priorAuthCaseNum)

    # take PA case entered after 2010 to avoid the null priorAuthStatus
    # there are PA cases with null priorAuthEnteredDate and null priorAuthStatus. These could be cases don't need priorAuth
    priorAuth <- priorAuth %>%
              dplyr::filter(priorAuthEnteredDt > "2010-01-01")


    priorAuth <-priorAuth %>%
            select(priorAuthCaseNum, priorAuthNumber, priorAuthDate, priorAuthEnteredDt, priorAuthEnteredTime,
                   priorAuthResult, priorAuthResult_Category, priorAuthReqDesc)
    
    return(priorAuth)
}

```
** Get Quadax appeal status **
Quadax writes the appeal status in appeal.txt
The file has all the appeal cases created GHI claims.
There are multiple rows for appeal cases processed through multiple levels.
Appeal case status updates is overwritten everytime there is an update.

A OLI can have multiple appeal cases, and each case can have multiple levels.

This function returns 3 views of appeal status
a) the appeal status table as given by Quadax
b) the appeal status wide format. span out the appeal level
c) the latest appeal level & detail per appeal case

```{r}

getAppeals <- function(folder, refresh = 0) {

    target <- "ODSProd01_Quadax_QDX_appeal.txt"

    if (refresh == 1) {
        con <-odbcDriverConnect(connection = "Driver={ODBC Driver 13 for SQL Server};trusted_connection=yes;
                               server=ODSProd01;
                               database=Quadax")
        sql <- paste(trimws(readr::read_lines(paste(sql_folder, "QDX_appeal.sql",sep=""))), collapse="\n")
        appeal_status <- sqlQuery(con, sql, stringsAsFactors = FALSE)
        write.table(appeal_status,paste(folder,target,sep=""), sep="|",row.names=FALSE)
        odbcClose(con)
    } else {
        appeal_status <- read.table(paste(folder,target,sep=""), sep="|", header=TRUE, stringsAsFactors = FALSE)
    }

    appeal_status$appealCaseNumber <- as.character(appeal_status$appealCaseNumber)
    
    # cast the appeal_status from long to wide format
    wide_Status <- dcast(appeal_status, appealCaseNumber~appealLvlCode, value.var=c("appealStatus"), fun=first)
    wide_status_desc <- dcast(appeal_status, appealCaseNumber~appealLvlCode, value.var=c("appealStatusDesc"), fun=first)
    wide_DenialDt <- dcast(appeal_status, appealCaseNumber~appealLvlCode, value.var=c("appealDenialLetterDt"), fun=first)
    wide_InsCode <- dcast(appeal_status, appealCaseNumber~appealLvlCode, value.var=c("appealInsCode"), fun=first)
    wide_EntryDt <- dcast(appeal_status, appealCaseNumber~appealLvlCode, value.var=c("appealEntryDt"), fun=first)
    wide_DenReason <- dcast(appeal_status, appealCaseNumber~appealLvlCode, value.var=c("appealDenReasonDesc"), fun=first)

    temp = c("_Status", "_DenialDt", "_InsCode","_EntryDt","_DenReason")
    for (i in seq_along(temp)) {
        temp_tlb <- paste("wide",temp[i],sep="")
        temp_col <- paste(names(get(temp_tlb))[2:length(names(get(temp_tlb)))],temp[i],sep="")
        setnames(get(temp_tlb),names(get(temp_tlb))[2:length(names(get(temp_tlb)))], temp_col)
    }

    appeal_status_wide <- list(wide_status_desc, wide_Status, wide_DenialDt, wide_InsCode, wide_EntryDt, wide_DenReason) %>%
                          Reduce(function(dtf1,dtf2) full_join(dtf1,dtf2), .)

    rm(list = ls()[grep("^wide_*", ls())])

    # determine the latest appeal level using Denial Letter Date
    last_appealLvl <- appeal_status %>%
                      group_by(appealCaseNumber) %>%
                      slice(which.max(appealDenialLetterDt)) %>%
                      select(appealCaseNumber,appealDenialLetterDt,appealEntryDt,
                             appealLvl, appealLvlCode, appealLvlDesc,
                             appealStatus, appealStatusDesc,
                             appealInsCode,
                             appealDenReason, appealDenReasonDesc)

    
    last_appealLvl <- setnames(last_appealLvl, c('appealCaseNumber', 'lastDenialLetterDt', 'lastappealEntryDt',
                                                     'lastappealLvlCode', 'LastAppealLevel', 'lastappealLvlDesc',
                                                     'lastappealStatusCode', 'lastappealStatus',
                                                     'lastappealInsCode',
                                                     'appealDenReasonCode', 'appealDenReasonDesc'))

    
    appeal_status$appealEntryDt <- ymd(appeal_status$appealEntryDt)
    appeal_status$appealDenialLetterDt <- ymd(appeal_status$appealDenialLetterDt)
    
    return(list(appeal_status,appeal_status_wide,last_appealLvl))
}

```

** Get Quadax appeal success information **
Everynight, Quadax extracts and summarizes information on completed appeals into the appealSuccess.txt
This file has completed appeals of OLI DOS since 2016-01-01.

```{r}
getAppealSuccess <- function(folder, refresh = 0) {

    target <- "ODSProd01_Quadax_QDX_complete_appeal_case.txt"

    if (refresh == 1) {
        con <-odbcDriverConnect(connection = "Driver={ODBC Driver 13 for SQL Server};trusted_connection=yes;
                               server=ODSProd01;
                               database=Quadax")
        sql <- paste(trimws(readr::read_lines(paste(sql_folder, "QDX_appealSuccess.sql",sep=""))), collapse="\n")
        complete_appeals <- sqlQuery(con, sql, stringsAsFactors = FALSE)
        write.table(complete_appeals,paste(folder,target,sep=""), sep="|",row.names=FALSE)
        odbcClose(con)
    } else {
        complete_appeals <- read.table(paste(folder,target,sep=""), sep="|", header=TRUE, stringsAsFactors = FALSE)
    }
    
    for (i in seq_along(QDX_GHI_Test_Code$QDX_Code)) {
        a <- which(complete_appeals$appealPH == QDX_GHI_Test_Code$QDX_Code[i])
        complete_appeals[a,'appealPH'] <- QDX_GHI_Test_Code$GHI_Code[i]
    }

    complete_appeals$appealTickNum <- as.character(complete_appeals$appealTickNum)
    complete_appeals$appealCaseNum <- as.character(complete_appeals$appealCaseNum)

    complete_appeals$appealRptDt <- ymd(complete_appeals$appealRptDt)
    complete_appeals$appealDOS <- ymd(complete_appeals$appealDOS)
    
    complete_appeals$appealAmtAplRec <- complete_appeals$appealAmtAplRec*-1
    #complete_appeals$appealAmtClmRec <- complete_appeals$appealAmtClmRec*-1
    
    return(complete_appeals)
}

```

