---
title: "OLI_Claim_Process"
output: html_document
---

Goal: To create a dataset that summarize the Claim process per OLI
1. SOMN request and result
2. DocuSign status
3. Prior Authorization request and result

This dataset provide the information to analysis and quantify Claim documentation and process issues.
Attempt to find out how the issues impacting reimbursement, claim denial, underpayment, etc.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This 

```{r read data}

#OLIDetail <- getOLIDetail('Claim_Process', DB_source_data, refresh)


SOMN_Cases <- getGHISOMNcase(DB_source_data,refresh=1)

# there are SOMN cases do not have a referece to an order nor OLI number
temp <- SOMN_Cases[is.na(SOMN_Cases$OrderNumber),]

select_col_a = c("OrderID", "OLIID" , "Test", "TestDeliveredDate", "Status"
               , "OrderStartDate", "QDXTicketNumber", "QDXCaseNumber"
               , "Tier2Payor", "Tier2PayorName", "Tier2PayorID"
               , "Tier4Payor", "Tier4PayorName", "Tier4PayorID", "FinancialCategory" ,"QDXInsPlanCode"
               , "Total Billed", "Total Outstanding", "Total Payment",  "Total Adjustment"
               , "Charged in Error"
               , "PayorPaid", "PatientPaid" , "Revenue Impact Adjustment"
               , "All other Adjustment", "GHI Adjustment", "Insurance Adjustment", "Refund & Refund Reversal"
               , "A1", "A2", "A3", "A4", "A5", "ER", "L1", "L2", "L3"
               , "appealDenReasonDesc", "appealResult"
               , "priorAuthDate", "priorAuthEnteredDt", "priorAuthEnteredTime", "priorAuthStatusDesc", "priorAuthReqDesc"
               )

# OR000750723  OR001040874

# run the Claim2Rev to get the current ticket/case before joinin prior auth.
Claim_Process_Status <- left_join(Claim2Rev[Claim2Rev$BusinessUnit=='Domestic',select_col_a], SOMN_Cases, by='OrderID')


target = 'Claim_Process_Status.txt'
write.table(Claim_Process_Status, file = paste(output_folder,target,sep=""), sep="|", row.names=FALSE, col.names=TRUE, na="")


```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
