---
title: "OLI_Claim2Rev"
output: html_notebook
---

Insert the purpose of this script

```{r Setup}
refresh = 1

## for Claim Ticket, amounts are reported per OLIID + Ticket Number
grp_var <- c('OLIID')
```

** Read Revenue Data from GHI **
### Get the Test revenue from EDWDB.fctRevenue table

```{r Read GHI Revenue Data}

Revenue <- getGHIRevenue('Claim2Rev', DB_source_data, refresh)
#('ClaimTicket', DB_source_data, refresh)

    # exploration
    a <- c(grep("^(?i)([^(OL)])",Revenue$OLIID), grep('^OL([^0-9])',Revenue$OLIID))
    sprintf("%d rows have null Order Line Item Id", sum(is.na(Revenue$OLIID)))
    sprintf("and %d rows have unconventional Order Line Item Id i.e. OLnnn format", length(a))

    a <- grep('^9+', Revenue$TicketNumber)    
    sprintf("%d rows have null Ticket Number", sum(is.na(Revenue$TicketNumber)))
    sprintf("however, %d rows have (-1) or (999999) Ticket Number", sum(sum(Revenue$TicketNumber=='-1'),length(a)))
    
Revenue[(which(is.na(Revenue$OLIID))),'OLIID'] <- "Unknown"

```

** get Test claim data **
Get the Test Claim data from Quadax stdClaim.txt. Quadax provides the inforamtion in a zip file to the FTP server every night.
The data is loaded every night into ODSProd01.
The sql select claim of date of service since 2015-10-01

```{r Read QDX Claim, Payment & Case Data}
Claim <- getQDXClaim('ClaimTicket', DB_source_data, refresh)
Pymnt <- getQDXPayment('ClaimTicket', DB_source_data, refresh)
Cases <- getQDXCases('QDXClaim_CaseStatus', DB_source_data, refresh)

```

** Cleaning the data **
1. drop the scenario either need checking, and not working for the OLI grain
   a. Claim without OLI reference
   b. Payment without OLI reference
   This script is to generate a dataset/report to track OLI bill amount, receipt and revenue. Transactions without OLI reference will not be picked up in the merging and joining.
   
2. Remove the top side adjustment from Revenue file.
   Finance are making some of the top side adjustment to actual OLIs, OLIs that fall into the same payor/country.
   A flag is utilized in 2016 to call out revenue rows of Revenue adjustment.
   New process was introduced in 2017, since then the revenue adjustment rows are not flagged.
   
Open: how to make use of the QDX Ticket transaction without reference to an OLI?
      how to make use of the GHI Revenue transaction that are reference to a 'fake' OLI?

```{r Clean data}

#Claim_wo_OLI <- Claim[(is.na(Claim$OLIID) | Claim$OLIID=='NONE'),]
Claim_wo_OLI <- nrow(Claim[(is.na(Claim$OLIID) | Claim$OLIID=='NONE'),])
print(paste (Claim_wo_OLI, " claim tickets have no OLI reference.", sep=""))
Claim <- Claim[(!((is.na(Claim$OLIID)) | (Claim$OLIID=='NONE'))),]

#Pymnt_wo_OLI <- Pymnt[(is.na(Pymnt$OLIID) | Pymnt$OLIID=='NONE'),]
Pymnt_wo_OLI <- nrow(Pymnt[(is.na(Pymnt$OLIID) | Pymnt$OLIID=='NONE'),])
print(paste (Pymnt_wo_OLI, " Payment ticket transactions have no OLI reference.", sep=""))
Pymnt <- Pymnt[(!((is.na(Pymnt$OLIID)) | (Pymnt$OLIID=='NONE'))),]

Revenue <- Revenue %>%
           dplyr::filter(Revenue$IsRevenueReconciliationAdjustment == 0)
```

** Read Order Line Detail data **
for OLI Claim2Rev, use the OLI Payor information from OLIDetail
for ClaimTicket2Rev, get the Ticket information from Revenue file. If the ticket payor information is not available, then patch it with the OLI Payor information.

```{r Read GHI Order Line Detail Data}

OLIDetail <- getOLIDetail('Claim2Rev', DB_source_data, refresh)
setnames(OLIDetail, 'CurrentTicketNumber','Orig_CurrentTicketNumber')

```

** find the Current QDX Ticket Number and Current QDX Case Number associated with an OLI **
From Claim, find the latest QDX Ticket number as the current QDX Ticket Number
Lookup the QDX case number for the current Ticket Number in Cases, and use it as the current QDX Case Number for the OLI
If there are multiple case numbers assoicated with the Ticket, take the max. value

For OLI that do not have a QDX Ticket, lookup the latest QDX Case Number in the Cases to be the current QDX Case Number
```{r}

TickCnt <- Claim %>%
         group_by (OLIID) %>%
         summarize(TickCnt = n_distinct(TicketNumber))

temp <- Claim %>%
        group_by(OLIID, TicketNumber) %>%
        slice(which.max(CaseNumber))         
    
QDX_CurrentTicket <- temp %>%
         group_by(OLIID) %>%
         slice(which.max(TicketNumber)) %>%
         select(OLIID, TicketNumber, CaseNumber, BillingCaseStatusSummary1, BillingCaseStatusSummary2, BillingCaseStatusCode, BillingCaseStatus)

setnames(QDX_CurrentTicket, c('TicketNumber','CaseNumber'),c('QDXTicketNumber','QDXCaseNumber'))


CaseCnt <- Cases %>%
           group_by(caseAccession) %>%
           summarize(CaseCnt = n_distinct(caseCaseNum))

QDX_CurrentCase <- Cases %>%
                   group_by(caseAccession) %>%
                   slice(which.max(caseCaseNum)) %>%
                   select(caseCaseNum, caseAccession)
```
** add the TickCnt, CaseCnt, QDX Current Ticket Number and QDX Current Case Number to OLIDetail **

```{r}

OLIDetail <- left_join(OLIDetail, TickCnt, by='OLIID')
OLIDetail <- left_join(OLIDetail, CaseCnt, by=c('OLIID'='caseAccession'))

OLIDetail <- left_join(OLIDetail, QDX_CurrentTicket, by='OLIID')
OLIDetail <- left_join(OLIDetail, QDX_CurrentCase, by=c('OLIID'='caseAccession'))

a <- which(is.na(OLIDetail$CurrentQDXCaseNumber))
OLIDetail[a,'QDXCaseNumber'] <- OLIDetail[a,'caseCaseNum']


##############

OLI_info <- OLIDetail %>%
            select(OrderID, OLIID, BilledCurrency, Test, TestDeliveredDate, OrderStartDate,
                   ##
                   QDXTicketNumber, QDXCaseNumber, TickCnt, CaseCnt,
                   Status, BillingCaseStatusCode, BillingCaseStatus,
                   BillingCaseStatusSummary1, BillingCaseStatusSummary2,
                   RevenueStatus, TestDelivered, IsClaim,  IsFullyAdjudicated,
                   Reportable, IsCharge,
                   ListPrice, ContractedPrice,
                   ##
                   Tier1Payor, Tier1PayorName, Tier1PayorID,
                   Tier2Payor, Tier2PayorName, Tier2PayorID,
                   Tier4Payor, Tier4PayorName, Tier4PayorID,
                   FinancialCategory, QDXInsPlanCode, LineOfBenefit,
                   ##
                   BusinessUnit, InternationalArea, Division, Country,
                   Territory, TerritoryRegion, TerritoryArea,
                   ##
                   OrderingHCPCity, OrderingHCPState, OrderingHCPCountry,
                   IsOrderingHCPCTR, IsOrderingHCPPECOS
                   ,
                   NodalStatus, ReportingGroup, RiskGroup,
                   EstimatedNCCNRisk, SubmittedNCCNRisk, FavorablePathologyComparison,
                   Specialty
                   )

#OLI_Utilization <-getOLIDetail('Utilization', DB_source_data, refresh)
#Summarized_Utilization <- OLI_Utilization %>%
#                          select(OLIID, NodalStatus, ReportingGroup, RiskGroup,
#                                 EstimatedNCCNRisk, SubmittedNCCNRisk, FavorablePathologyComparison,
#                                 Specialty)

# update the wording for Micromets
a <- which(OLI_info$NodalStatus == 'Micromets (pN1mi: 0.2 - 2.0mm)')
OLI_info[a,"ReportingGroup"] <- OLI_info[a,"NodalStatus"]


rm(CaseCnt, TickCnt, QDX_CurrentCase, QDX_CurrentTicket)


```

```{r}
```


** Summarize the Revenue data by grp_var: OLIID **
```{r Summarize Revenue}
print(paste('OLI_Claim2Rev.R : summarize Revenue numbers start',Sys.time(), sep = " "))

Summarize_Revenue_group<-
    Revenue %>%
    group_by_(.dots=grp_var) 

Summarized_Revenue <- 
    Summarize_Revenue_group%>%
    summarize(Revenue = sum(TotalRevenue),
              AccrualRevenue = sum(TotalAccrualRevenue),
              CashRevenue = sum(TotalCashRevenue),
              USDRevenue = sum(TotalUSDRevenue),
              USDAccrualRevenue = sum(TotalUSDAccrualRevenue),
              USDCashRevenue = sum(TotalUSDCashRevenue))

print(paste('OLI_Claim2Rev.R : summarize Revenue numbers finish',Sys.time(), sep = " "))

```


** Summarize the Claim (Charge, Payment, Adjustment, Outstanding) by grp_var: OLI**
Quadax provides claim charge, total amount received per ticket, total amount adjusted per ticket and current ticket balance in the Claim file.
At all time, per a ticket, the charge amount = sum of (Received amount + adjustment amount + ticket balance)

For GHI Payor Analytics report, we reverse the sign of received amount, adjustment amount. 

```{r Summarize Claim}

print(paste('OLI_Claim2Rev.R : summarize Claim charge and outstanding numbers start',Sys.time(), sep = " "))

temp = c('ClmAmtRec','ClmAmtAdj')
for (i in seq_along(temp)) {
    Claim[temp[[i]]] <- Claim[temp[[i]]] *-1
}


## loading plyr mess up the group by in dplyr
Summarized_Claim <-
    Claim %>%
    group_by_(.dots=grp_var) %>%
    summarize(Charge = sum(TXNAmount),
#              Payment_amt = sum(ClmAmtRec),
#              Adjust_amt = sum(ClmAmtAdj),
              'Total Outstanding' = sum(ClmTickBal))

print(paste('OLI_Claim2Rev.R : summarize Claim charge and outstanding numbers finish', Sys.time(), sep = " "))

# nrow(unique(Claim, by = c('OLIID','TicketNumber'))) # not matching - this is from data.table, returning a data.table with duplicated rows removed. This works with Keyed vector..need to read more. 
# to count # of unique combination 
# uniqueN(Claim, by = c('OLIID','TicketNumber')) # mactching number
# nrow(unique(Claim[c('OLIID','TicketNumber')])) # matching number
```

** Summarize the Payment **
For Payor Analytics & reporting, reverse the sign for all Payment TXNAmount and Adjustment (except Refund) TXNAmount.

Then summarize the payment and adjustment amounts.
Total adjustment for an OLI are the sum of 'AD' and 'AC' transaction, excluding CIE and Refund.
CIE is adjustment to the charges; Refund is adjustment to Payment.

OL000755178, OL000754736,OL000754587 
multi ticket: OL000613861, OL000739220, OL000740430


```{r Summarize Payment & Adjustment}

print(paste('OLI_Claim2Rev.R : summarize Payment & Adjustment numbers start',Sys.time(), sep = " "))

# flipping the sign of adjustments except Refund
a <- which((!is.na(Pymnt$GHIAdjustmentCode)) & (Pymnt$GHIAdjustmentCode != 'GH04'))
Pymnt[a,"TXNAmount"] <- Pymnt[a,"TXNAmount"] * -1

# flip the sign of Payor & Patient payment
a <- which(Pymnt$TXNType %in% c('RI',"RP"))
Pymnt[a,"TXNAmount"] <- Pymnt[a,"TXNAmount"] * -1

Summarized_Payor_Pymnt <- Pymnt[Pymnt$TXNType=='RI',] %>%
                          group_by_(.dots=grp_var) %>%
                          summarize(PayorPaid = sum(TXNAmount))

Summarized_Patient_Pymnt <- Pymnt[Pymnt$TXNType=='RP',] %>%
                            group_by_(.dots=grp_var) %>%
                            summarize(PatientPaid = sum(TXNAmount))

# calculate the total adjustment, excluding charge in error (GH04) and refund & refund reversal (GH09)
a <- which( Pymnt$TXNType %in% c('AD','AC') &
            (Pymnt$GHIAdjustmentCode != 'GH04' & Pymnt$GHIAdjustmentCode != 'GH09')
          )
Summarized_Adjustment <- Pymnt[a,] %>%
                         group_by_(.dots=grp_var) %>%
                         summarize('Total Adjustment' = sum(TXNAmount))


# calculate the subTotal per Adjustment group
a <- which(Pymnt$TXNType %in% c('AD','AC') & Pymnt$OLIID != '')
temp <- melt(Pymnt[a,c(grp_var,'AdjustmentGroup','TXNAmount')], id.vars=c(grp_var,'AdjustmentGroup'))
Summarized_Adj_group <- dcast(temp, ...~variable, sum, na.rm=TRUE)
Summarized_Adj_group <- dcast(Summarized_Adj_group,
                              paste(paste(grp_var,collapse = "+"),"AdjustmentGroup",sep="~"),
                              value.var = 'TXNAmount')

rm(temp)
print(paste('OLI_Claim2Rev.R : summarize Payment & Adjustment numbers finish',Sys.time(), sep = " "))

```

** Construct the Claim2Rev dataset **
Claim2Rev provides summarized data per OLI.
It includes the OLI Id, Test, Payor & Plan, Claim amt, Receipt (Payment, Adjustment, Outstanding), Recoginized Revenue amt.

```{r combine summarized data into Claim2Rev}

print(paste('OLI_Claim2Rev.R : join the summarized numbers into ClaimTicket2Rev report start',Sys.time(), sep = " "))

## Genreate a report for each OLI + Ticket Number, the summary of Claim (charge & outstanding), Payment, Adjustment
#Summarized_Utilization,
Claim2Rev<-
list(OLI_info,
     Summarized_Revenue,
     Summarized_Claim,
     Summarized_Payor_Pymnt,Summarized_Patient_Pymnt,
     Summarized_Adjustment, Summarized_Adj_group) %>%
    Reduce(function(dtf1,dtf2) left_join(dtf1,dtf2), .)
#full

temp = c('Charge','Charged in Error', 'PayorPaid','PatientPaid', 'Refund & Refund Reversal',
         "Revenue", "AccrualRevenue", "CashRevenue",
         "USDRevenue", "USDAccrualRevenue", "USDCashRevenue",
         "Total Outstanding",
         "All other Adjustment", "GHI Adjustment", "Insurance Adjustment", "Revenue Impact Adjustment",
         "TickCnt")
for (i in seq_along(temp)) {
    #print(temp[[i]])
    a <- which(is.na(Claim2Rev[temp[[i]]]))
    Claim2Rev[a, temp[[i]]] <- 0.00
}

Claim2Rev <- Claim2Rev %>%
             mutate('Total Payment' = PayorPaid + PatientPaid + `Refund & Refund Reversal`)

Claim2Rev <- Claim2Rev %>%
             mutate('Total Billed' = Charge + `Charged in Error`)

#target = 'Claim2Rev.txt'
#write.table(Claim2Rev, file = paste(output_folder,target,sep=""), sep="|", row.names=FALSE, col.names=TRUE, na="")

rm(list = ls()[grep("^Summarize*", ls())])

print(paste('OLI_Claim2Rev.R : join the summarized numbers into ClaimTicket2Rev report finish',Sys.time(), sep = " "))

```

** Read appeal status data **
and make a wide version with 1 appeal case per row, span appeal levels 

```{r}
appeal_status_list <- getAppeals(DB_source_data, refresh)

appeal_status_wide <- data.frame(appeal_status_list[2])
latest_appealLvl <- data.frame(appeal_status_list[3])

complete_appeal <- getAppealSuccess(DB_source_data, refresh)

```


** Enhance Claim2Rev with appeal and PA data **

```{r}
select_col <- c('appealCaseNumber',
                'A1','A2','A3','A4','A5','ER','L1','L2','L3',
                'A1_Status','A2_Status','A3_Status','A4_Status','A5_Status','ER_Status','L1_Status','L2_Status','L3_Status')
Claim2Rev <-  left_join(Claim2Rev, appeal_status_wide[,select_col], by=c('QDXCaseNumber' = 'appealCaseNumber'))

select_col = c('appealCaseNumber', 'lastappealEntryDt',
               'LastAppealLevel',
               'lastappealStatus',
               'appealDenReasonCode','appealDenReasonDesc')
Claim2Rev <-  left_join(Claim2Rev, latest_appealLvl[,select_col], by=c('QDXCaseNumber' = 'appealCaseNumber'))

select_col = c('appealCaseNum','appealSuccess',
               'appealAmtChg','appealAmtChgExp','appealAmtAllow',
               'appealAmtClmRec',
               'appealAmt','appealAmtAplRec',
               'appealRptDt','appealCurrency')


Claim2Rev <- left_join(Claim2Rev, complete_appeal[,select_col], by=c('QDXCaseNumber' = 'appealCaseNum'))
#Claim2Rev_2 <- left_join(Claim2Rev_2, complete_appeal[,col_complete_appeal], by=c('QDXTicketNumber' = 'appealTickNum'))

## calculate the appealResult
Claim2Rev[which(Claim2Rev$appealSuccess==1),'appealResult'] <- 'Success'
Claim2Rev[which(Claim2Rev$appealSuccess==0),'appealResult'] <- 'Failed'

# Scenario : appealSuccess is null but there is appeal Den Reason -> appeal is in process
a <- is.na(Claim2Rev$appealSuccess)
b <- is.na(Claim2Rev$appealDenReason)
Claim2Rev[which(a & !b),'appealResult'] <- 'In Process'

QDX_complete_appeal_status <- c('Completed','Final Review','Due from Patient')

# if Billing Status is in complete status -> conclude the appeal is removed
a <- (Claim2Rev$appealResult == 'In Process')
b <- (Claim2Rev$BillingCaseStatusSummary2 %in% QDX_complete_appeal_status)
Claim2Rev[which(a & b),'appealResult'] <- 'Removed'

## 'correct' BillingCaseStatusSummary2

# Scenario appeal case is open with the current ticket for the OLI, BillignCaseStatusSummary2 is not appeal
c <- Claim2Rev$BillingCaseStatusSummary2 == 'Appeals'
Claim2Rev[which(a & !b & !c), 'BillingCaseStatusSummary2'] <- 'Appeals'

# Scenario appealResult is either success or fail, Billing Status is not in the QDX_complete_appeal_status,
a <- Claim2Rev$appealResult %in% c('Failed','Success')
Claim2Rev[which(a & !b),'BillingCaseStatusSummary2'] <- 'Final Review'
Claim2Rev[which(a & !b),'BillingCaseStatus'] <- 'Final Review'

a <- is.na(Claim2Rev$appealResult)
Claim2Rev[which(a & c),'BillingCaseStatusSummary2'] <- 'Claim in Process'

rm(appeal_status_list)
```
** Get Prior Authorization**

case 1146991 has " in the prior number freeform field

```{r}
QDX_PA_Case <- getQDXPA(DB_source_data, refresh)

select_col <- c('priorAuthCaseNum','priorAuthDate','priorAuthEnteredDt','priorAuthEnteredTime',
                'priorAuthResult', 'priorAuthResult_Category','priorAuthReqDesc')

Claim2Rev <- left_join(Claim2Rev, QDX_PA_Case[,select_col], by=c('QDXCaseNumber' = 'priorAuthCaseNum'))


# add a PA_Category with 'Not Requested' to flag those OLIs which PA is not requested.
Claim2Rev$QDX_priorAuthResult_Category <- Claim2Rev$priorAuthResult_Category
a <- is.na(Claim2Rev$priorAuthResult_Category)
Claim2Rev[which(a),'priorAuthResult_Category'] <- "Not Requested"

```


**Create a OLI detail jonural entry**
```{r TXN Detail}

#select_col <- c("OLIID","Total Billed","Total Outstanding","Total Payment","Revenue")
select_col <- c("OLIID","PayorPaid","PatientPaid","Total Outstanding")
OLI_TTXN<-melt(Claim2Rev[,select_col],
               id.vars=("OLIID"), variable_name="TXNType", value_name="TXNAmount")
setnames(OLI_TTXN,c("value","variable"),c("TXNAmount","TXNTypeDesc"))

OLI_TTXN <- mutate(OLI_TTXN, TXNCategory = 'Receipts', TXNSubCategory = 'Payment')

levels(OLI_TTXN$TXNTypeDesc)[match("Total Outstanding",levels(OLI_TTXN$TXNTypeDesc))] <- 'Outstanding'
OLI_TTXN[OLI_TTXN$TXNTypeDesc == 'Outstanding','TXNSubCategory'] <- 'Outstanding'


# retrieve adjusment transaction
Adjustment_TTXN <- Pymnt %>%
                   dplyr::filter(TXNType %in% c('AC','AD')) %>%
                   group_by_(.dots=c(grp_var,'AdjustmentGroup','GHIAdjustmentCode','CategoryDesc','QDXAdjustmentCode','Description')) %>%
                   summarize(sum_TXN = sum(TXNAmount))
setnames(Adjustment_TTXN, c('sum_TXN'),c('TXNAmount'))
Adjustment_TTXN <- Adjustment_TTXN %>%
                   mutate(TXNTypeDesc = paste(GHIAdjustmentCode, ":",CategoryDesc,sep=""),
                          TXNCategory = 'Receipts',
                          TXNSubCategory = 'Adjustment')

Adjustment_TTXN[Adjustment_TTXN$GHIAdjustmentCode=='GH04','TXNCategory'] <- 'Billing'
Adjustment_TTXN[Adjustment_TTXN$GHIAdjustmentCode=='GH04','TXNSubCategory'] <- 'Charged in Error'
Adjustment_TTXN[Adjustment_TTXN$GHIAdjustmentCode=='GH09','TXNSubCategory'] <- 'Payment'

OLI_TXN <-
list(OLI_TTXN,
     Adjustment_TTXN) %>%
    Reduce(function(dtf1,dtf2) bind_rows(dtf1,dtf2), .)

## adding OLI_Info (w/ Payor)
OLI_TXN <- OLI_TXN %>%
           dplyr::filter(TXNAmount != 0.0) %>%
           dplyr::filter(OLIID!="") %>%
           arrange(OLIID)

select_col <- c('OLIID','Test','TestDeliveredDate'
                ,'Tier1Payor','Tier2Payor','Tier2PayorID','Tier4Payor','FinancialCategory','LineOfBenefit'
                ,'TerritoryRegion','OrderingHCPState')

OLI_TXN <- left_join(OLI_TXN, OLI_info[,select_col], by='OLIID')

setnames(OLI_TXN, c('FinancialCategory'), c('Financial Category'))

rm(list = ls()[grep("*_TTXN*", ls())])
```

** Add the Top Payors, BCBS, eviCore flag **

```{r}

prep_file_name <- "Payor-ViewSetAssignment.xlsx"
Payor_View <- read.xlsx(paste(prep_file_path, prep_file_name, sep=""), sheetName ="SetAssignment",  colIndex=c(1:3),
                        stringsAsFactors=FALSE, header=TRUE, colClasses=c('character','character','character'))

create_set <- unique(Payor_View$Set)
for (i in seq(length(create_set))) {
        
    code <- Payor_View %>%
            dplyr::filter(Set == create_set[i]) %>%
            select(Tier2PayorID)
        
    Claim2Rev[Claim2Rev$Tier2PayorID %in% code$Tier2PayorID, create_set[i]] <-'1'
    OLI_TXN[OLI_TXN$Tier2PayorID %in% code$Tier2PayorID, create_set[i]] <-'1'
}

rm(code, Payor_View)
######
target = 'Claim2Rev.txt'
write.table(Claim2Rev, file = paste(output_folder,target,sep=""), sep="|", row.names=FALSE, col.names=TRUE, na="")



target = 'OLI_TXN_Detail.txt'
write.table(OLI_TXN, file = paste(output_folder,target,sep=""), sep="|", row.names=FALSE, col.names=TRUE, na="")

```

