---
title: "Pre-Claim_Process"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Pre Claim Process

Purpose: to prepare a dataset that contains the data & information on Quadax pre claim process for Test Order received in 2017
(order start date >= 2017-01-01).

We need the information to answer:
1. Who is the payor/plan/test required pre-claim documentation
2. Have we succeed or failed to gather the pre-claim documents such as prior authorization
3. What are the reason of failling to obtain prior authorization? What should be done to fix it. - not in phase 1 as I am not reading in the worklist.


Then we take action to reduce pre claim failure.

Data sources:
1. Prior Authorization type & status: Quadax priorAuth.txt, virtualSelfDescInfo.txt
2. QDX Case number, Ticket number to OLI ID mapping, and billing case status: Quadax Cases.txt
3a. Order Line Item detail, SFDC Order Status : GHI EDW StagingDB.Analytics.stgOrderDetail
    Requirement to EDW, append the prior authorization type and status by case # and current ticket number.


```{r source data}

# reading QDX data
# prior authorization & status

QDX_PA <- getQDXPA(QDX_zip_data,0)
Cases <- getQDXCases('QDXClaim_CaseStatus', DB_source_data, 0)

#OLI_detail
#OLIDetail <- getOLIDetail('Claim2Rev', folder, 0)
#call OLI_Claim2Rev.R to get the Claim2Rev dataset

# select the OLI entered since 2017-01-01 and Test Delivered date is not null
OLI_info <- Claim2Rev %>%
            dplyr::filter((OrderStartDate >= '2017-01-01') & !(is.na(TestDeliveredDate)))

#OLI_info <- OLIDetail %>%
#            filter((OrderStartDate >= '2017-01-01') & !(is.na(TestDeliveredDate))) %>%
#            select(OrderID, OLIID, Test, OrderStartDate, TestDeliveredDate, CurrentTicketNumber,
#                  Tier1Payor, Tier2Payor, Tier4Payor, FinancialCategory,
#                   Territory, TerritoryArea, TerritoryRegion,
#                   OrderingHCPState, OrderingHCPCountry, OrderingHCOState, OrderingHCOCountry, Specialty
#                   )

#OLICriteria <- getOLIDetail('utilization', folder,0)


# Cases have the OLI-QDXCaseNumber-QDXTicketNumber mapping. Cases have 0..1 PA Case
# join the PA case info to Cases.
# priorAuth have cases that do not have ticket number. it can be because priorAuth case is not required and no priorAuthCase is opened, or ticket has not be issued or system do not update the issued ticket number (then ticket number = 0)
QDX_PA <- left_join(Cases, QDX_PA, by=c("caseCaseNum"="priorAuthCaseNum"))

# for output data set for users, remove the unused columns. These columns are useful for debugging.
QDX_PA <- QDX_PA %>%
          select(-c(caseEntryYrMth, BillingCaseStatusSummary1, priorAuthTicketNum))

# in OLI_info, there are pre-claim and claim in progress status.
# if ticket number is null, these are likely the pre-claim OLI
# when QDX process a claim, a ticket number is issued.
# pull the case & PA status information if ticket is issued
PreClaim_Status <- left_join(OLI_info, QDX_PA, by=c("OLIID"="caseAccession", "CurrentTicketNumber"="caseTicketNum"))


target = 'PreClaim_Status.txt'
write.table(PreClaim_Status, file = paste(folder,target,sep=""), sep="|", row.names=FALSE, col.names=TRUE, na="")


```
